Article Title

### 2013-10-30 sections/Figure2.tex
Continuing to integrate Alex's changes.

\begin{figure}[htp]
\centering
\includegraphics[width=0.5\textwidth]{figures/Figure2.pdf}
\caption{
Graphical models corresponding to the low-dimensional targets of the four regularization schemes used in the paper.
\textbf{A}: A diagonal matrix corresponds to a Gaussian graphical model with no dependencies.
\textbf{B}: In factor analysis, observed nodes are assumed to be influenced by several latent units (``factors") but are otherwise independent.
\textbf{C}: Graphical model with conditional dependencies between some pairs of observed neurons, no latent units. 
\textbf{D}: Graphical model with conditional dependencies between some pairs of observed neurons and dense interactions with a few latent units.
}\label{fig:02}
\end{figure}

>>>>

\begin{figure}[htp]
\centering
\includegraphics[width=0.5\textwidth]{figures/Figure2.pdf}
\caption{
Graphical models corresponding to the low-dimensional targets of the four regularization schemes used in the paper. It assumed that all interactions are linear, \emph{i.e.}\;the mean firing rate of any neuron can be computed by a linear combination of the firing rates of other neurons and latent units.
\textbf{A}: ``Independent.'' A population with no interactions corresponds to the diagonal covariance matrix.
\textbf{B}: ``Latent factors.'' Observed nodes are assumed to be influenced by several latent units (``factors") but are otherwise independent.
\textbf{C}: ``Sparse.'' Partial correlations between a subset of pairs of observed neurons, zero partial correlations between all other pairs.  
\textbf{D}: ``Sparse+latent.''  Partial correlations between a subset of pairs of observed neurons and a few latent factors interacting with the entire population. 
}\label{fig:02}
\end{figure}

### 2013-10-30 sections/Results.tex
Continuing to integrate Alex's changes.

To verify our approach and to illustrate the performance of our four regularized estimators and the sample covariance estimator, we constructed five model populations with different underlying structures. Each population contained 100~neurons. The first four populations matched the low-dimensional structure of our four estimators: independent (Fig.~2\,A), low-rank (Fig.~2\,B), sparse inverse (Fig.~2\,C) and low-rank combined with sparse inverse (Fig.~2\,D). \Acomment{Integrate schematics from Fig.~1 into this figure (make it the first row) for better correspondence} In addition, we considered a fifth population that had no low-dimensional structure (Fig.~2\,E).

@@

We recorded the calcium activity of dense populations of neurons in the supragranular layers in primary visual cortex of anesthetized mice using fast random-access 3D scanning two-photon microscopy \cite{Stosiek:2003,Reddy:2005}. We presented numerous repetitions of full-field drifting gratings (Fig. 1A and 1B) to the eye contralateral to the imaged site. This technique allowed us to record from a large number (150--350) of cells in a small volume of cortical tissue ($200\times200\times100$ $\mu$m$^3$) in layers 2/3 and 4. We deconvolved somatic calcium signals using sparse nonnegative deconvolution \cite{Vogelstein:2010} (Fig.\;1C and 1D) and subtracted the average stimulus response to remove effects of the stimulus. From this residual response we computed the sample noise covariance matrix (Fig.\;1E).

In such highly localized populations both direct interactions between cells and common diffuse inputs are likely to contribute to the overall population variability. At the same time, most correlations are relatively small (Fig.~1\,E), suggesting that a simple shrinkage towards independence may provide a sufficiently well regularized estimate. By comparing the performance of our differently regularized estimators we can gain insights into which of these aspects are important in our data.

>>>>

To verify our approach and to illustrate the performance of the four regularized estimators, we constructed five model populations with different underlying structures. Each population contained 100~neurons. The first four populations matched the low-dimensional structure of our four estimators: independent (Fig.~\ref{fig:03}A), low-rank (Fig.~\ref{fig:03}B), sparse inverse (Fig.~\ref{fig:03}C) and low-rank combined with sparse inverse (~\ref{fig:03}D). \Acomment{Integrate schematics from Fig.~1 into this figure (make it the first row) for better correspondence} In addition, we considered a fifth population that had no low-dimensional structure (Fig.~\ref{fig:03}\,E).

\input{sections/Figure3.tex}

@@

We recorded the calcium activity of dense populations of neurons in the supragranular layers in primary visual cortex of anesthetized mice using fast random-access 3D scanning two-photon microscopy \cite{Stosiek:2003,Reddy:2005}. We presented numerous repetitions of full-field drifting gratings (Fig.~\ref{fig:01}A and \ref{fig:01}B) to the eye contralateral to the imaged site. This technique allowed us to record from a large number (150--350) of cells in a small volume of cortical tissue ($200\times200\times100$ $\mu$m$^3$) in layers 2/3 and 4. We deconvolved somatic calcium signals using sparse nonnegative deconvolution \cite{Vogelstein:2010} (Fig.~\ref{fig:01}C and \ref{fig:01}D) and subtracted the average stimulus response to remove effects of the stimulus. From this residual response we computed the sample noise covariance matrix (Fig.~\ref{fig:01}E).

\input{sections/Figure1.tex}

In such highly localized populations both direct interactions between cells and common diffuse inputs are likely to contribute to the overall population variability. At the same time, most correlations are relatively small (Fig.~\ref{fig:01}E), suggesting that a simple shrinkage towards independence may provide a sufficiently well regularized estimate. By comparing the performance of our differently regularized estimators we can gain insights into which of these aspects are important in our data.
